A Hybrid Ensemble Learning Approach to Star-galaxy Classification

### 2015-04-15 paper/main.tex
Add purity in vvds w1 figures.

%\begin{figure*}
%  \begin{minipage}[t]{0.49\linewidth}
%    \includegraphics[width=\textwidth]{figures/purity_mag.eps}
%    \caption{Purity of morphological separation,
%             TPC, and BMC techniques in 
%             as a function of the $i$-band magnitude.
%             The top panel shows the histogram of objects in the test data set.
%             The second panel shows the fraction of stars
%             as a function of magnitude. The error bars are Poisson.
%             The bottom two panels compare
%             the galaxy and star purity for morphological separation, TPC,
%             and BMC techniques as a function of magnitude.
%             The error bars for completeness and purity are not shown for
%             clarity, but they are approximately 10 percent.}
%    \label{fig:purity_mag}
%  \end{minipage}
%  \hfill
%  \begin{minipage}[t]{0.49\linewidth}
%    \includegraphics[width=\textwidth]{figures/purity_z.eps}
%    \caption{The same figures as Figure~\ref{fig:purity_mag},
%             but as a function of photometric redshift estimate
%             (photo-$z$).}
%    \label{fig:purity_z}
%  \end{minipage}
%\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_mag.eps}
  \caption{Purity of morphological separation,
           TPC, and BMC techniques in 
           as a function of the $i$-band magnitude.
           The top panel shows the histogram of objects in the test data set.
           The second panel shows the fraction of stars
           as a function of magnitude. The error bars are Poisson.
           The bottom two panels compare
           the galaxy and star purity for morphological separation, TPC,
           and BMC techniques as a function of magnitude.
           The error bars for completeness and purity are not shown for
           clarity, but they are approximately 10 percent.}
  \label{fig:purity_mag}
\end{figure}

@@

\begin{figure*}
  \begin{minipage}[t]{0.49\linewidth}
    \includegraphics[width=\textwidth]{figures/som_colors_cut.eps}
    \caption{The same figure as Figure~\ref{fig:som_colors_cut}
        but for the BMC technique applied to the four individual methods
        trained with the CFHTLenS data in the VVDS W1 field
        with $i < 22$.}
    \label{fig:som_colors_cut}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.49\linewidth}
    \includegraphics[width=\textwidth]{figures/weights_cut.eps}
    \caption{The same figure as FIgure~\ref{fig:weights_cut}
        but for the BMC technique applied to the four invidiual methods
        trained with the CFHTLenS data in the VVDS W1 field
        with $i < 22$.}
    \label{fig:weights_cut}
  \end{minipage}
\end{figure*}

In Figure~\ref{fig:weights_cut}, we again show the $10\times10$
two-dimensional weight map defined by the SOM.
It seems that \texttt{TPC} performs well
in most of the parameter space.
When the quality of training data is relatively poor,
the performance of data driven algorithms will decrease,
while the performance of template fitting algorithms such as \text{HB}
is independent of training data.
Thus, it is perhaps not surprising that
BMC algorithm now uses information from \texttt{HB},
whereas it assigned almost no weight to \texttt{HB}
when we had a high-quality training data.
Another interesting pattern is that
\texttt{SOMc} and morphological separation seem complementary;
\texttt{SOMc} is weighted most strongly at fainter magnitudes,
while the morphological separation method
is weighted most strongly at brighter magnitudes.
It is not surprising that the morphological separation method
performs best at bright magnitudes,
and BMC uses almost no morphological information at faint magnitudes.

%\begin{figure*}
%  \begin{minipage}[t]{0.49\linewidth}
%    \includegraphics[width=\textwidth]{figures/purity_mag_cut.eps}
%    \caption{Purity of morphological separation,
%             TPC, and BMC techniques in 
%             Table~\ref{table:metrics_vvds}
%             as a function of the $i$-band magnitude.
%             The top panel shows the fraction of stars
%             as a function of magnitude.
%             the galaxy and star purity for TPC and BMC techniques.
%             The bottom two panels show
%             the galaxy and star purity for morphological separation
%             and BMC technique.
%             We use the same threshold values from 
%             Figure~\ref{fig:purity_mag} in the bottom four panels}.
%    \label{fig:purity_mag_cut}
%  \end{minipage}
%  \hfill
%  \begin{minipage}[t]{0.49\linewidth}
%    \includegraphics[width=\textwidth]{figures/purity_z.eps}
%    \caption{The same figures as Figure~\ref{fig:purity_mag},
%             but as a function of photometric redshift estimate
%             (photo-$z$).}
%    \label{fig:purity_z}
%  \end{minipage}
%\end{figure*}

We present the star and galaxy purity values
of Table~\ref{table:metrics_vvds} as a function of
$i$-band magnitude in Figure~\ref{fig:purity_mag}.
It is clear that BMC outperforms both
morphological separation and TPC classification techniques
over all magnitudes.
The galaxy purity of BMC is significantly better
than that of TPC at bright magnitudes, $i\lesssim21.5$,
while they are similar at faint magnitudes.
The star purity of BMC shows improvement over that of TPC
at faint magnitudes,
while they are similar at bright magnitudes.
As suggested by the weight maps in Figure~\ref{fig:weights_cut},
BMC can accomplish this by combining information from
all base classifiers,
\eg giving more weight to the morphological separation method
at bright magnitudes.
We can also see in the bottom two panels that
the performance of morphological separation suffers
at intermediate magnitudes $21\lesssim i \lesssim23$,
while BMC shows consistently better performance
over all magnitude ranges.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_mag.eps}
  \caption{Purity of morphological separation,
           TPC, and BMC techniques
           as a function of the $i$-band magnitude.
           The top panel shows the histogram of objects in the test data set.
           The second panel shows the fraction of stars
           as a function of magnitude. The error bars are Poisson.
           The bottom two panels compare
           the galaxy and star purity for morphological separation, TPC,
           and BMC techniques as a function of magnitude.
           The error bars for completeness and purity are not shown for
           clarity, but they are approximately 10 percent.}
  \label{fig:purity_mag}
\end{figure}

@@

\begin{figure*}
  \begin{minipage}[t]{0.49\linewidth}
    \includegraphics[width=\textwidth]{figures/som_colors_cut.eps}
    \caption{The same figure as Figure~\ref{fig:som_colors}
        but for the BMC technique applied to the four individual methods
        trained with the CFHTLenS data in the VVDS W1 field
        with $i < 22$.}
    \label{fig:som_colors_cut}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.49\linewidth}
    \includegraphics[width=\textwidth]{figures/weights_cut.eps}
    \caption{The same figure as Figure~\ref{fig:weights}
        but for the BMC technique applied to the four invidiual methods
        trained with the CFHTLenS data in the VVDS W1 field
        with $i < 22$.}
    \label{fig:weights_cut}
  \end{minipage}
\end{figure*}

In Figure~\ref{fig:weights_cut}, we again show the $10\times10$
two-dimensional weight map defined by the SOM.
%It seems that \texttt{TPC} performs well
%in most of the parameter space.
\textcolor{blue}{When the quality of training data is relatively poor,
the performance of data driven algorithms will decrease,
while the performance of template fitting algorithms such as \texttt{HB}
is independent of training data.
Thus, comparing the weight maps of Figure~\ref{fig:weights}
and Figure~\ref{fig:weights_cut},
it is perhaps not surprising that
BMC algorithm now uses more information from
morphological separation and \texttt{HB},
while it uses considerably less information from TPC.
%Another interesting pattern is that
%\texttt{SOMc} and morphological separation seem complementary;
%\texttt{SOMc} is weighted most strongly at fainter magnitudes,
%while the morphological separation method
%is weighted most strongly at brighter magnitudes.
It is not surprising that the morphological separation method
performs best at bright magnitudes,
and BMC assigns more weight to \texttt{HB} at fainter magnitudes.}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_mag_cut.eps}
  \caption{Purity as a function of the $i$-band magnitude
           for morphological separation, TPC, and BMC techniques
           in the VVDS W1 field with $i < 22$.
           We repat in the top panel shows the histogram of objects
           in the test data set.
           The second panel shows the fraction of stars
           in the VVDS W1 and W4 fields.
           The error bars are Poisson.
           The bottom two panels compare
           the galaxy and star purity for morphological separation, TPC,
           and BMC techniques as a function of magnitude.
           The error bars for completeness and purity are not shown for
           clarity, but they are approximately 10 percent.}
  \label{fig:purity_mag_cut}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_z_cut.eps}
  \caption{The same figures as Figure~\ref{fig:purity_mag_cut},
           but as a function of photo-$z$.}
  \label{fig:purity_z_cut}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_g-r_cut.eps}
  \caption{The same figure as Figure~\ref{purity_mag_cut},
           but as a function of $g-r$ color.}
  \label{fig:purity_g-r_cut}
\end{figure}

We present the star and galaxy purity values
of Table~\ref{table:metrics_vvds} as a function of
$i$-band magnitude in Figure~\ref{fig:purity_mag_cut}.
It is clear that BMC outperforms both
morphological separation and TPC classification techniques
over all magnitudes.
The galaxy purity of BMC is significantly better
than that of TPC at bright magnitudes, $i\lesssim21.5$,
while they are similar at faint magnitudes.
The star purity of BMC shows improvement over that of TPC
at faint magnitudes,
while they are similar at bright magnitudes.
As suggested by the weight maps in Figure~\ref{fig:weights_cut},
BMC can accomplish this by combining information from
all base classifiers,
\eg giving more weight to the morphological separation method
at bright magnitudes.
We can also see in the bottom two panels that
the performance of morphological separation suffers
at intermediate magnitudes $21\lesssim i \lesssim23$,
while BMC shows consistently better performance
over all magnitude ranges.
